---
title: "Calculation of Physiological Metrics"
author: "Serena Hackerott"
date: "1/1/2024"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
    toc_float: yes
---

# Setup

```{r Setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


### Load Packages
```{r}
##Install Packages if Needed
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("plyr")) install.packages("plyr")

##Load Packages
library(ggplot2) #Required for ggplots
library(plyr) #Required for rename function
```


### Graphing Parameters
```{r}
#Note: Run "Graphing Parameters" section from 01_ExperimentalSetup.Rmd file
```


# Sample Data and Metadata

### Load and Organize Data
```{r}
####Load Data

Prot<-read.csv("Data/Protein.csv", header=TRUE)
Bio<-read.csv("Data/Biomass.csv", header=TRUE)
Sym<-read.csv("Data/Symbionts.csv", header=TRUE)
Chl<-read.csv("Data/Chlorophyll.csv", header=TRUE)
PAM<-read.csv("Data/PAMData.csv", header=TRUE)
PAM_Meta<-read.csv("Data/PAMMeta.csv", header=TRUE)
BCA.Stand<-read.csv("Data/BCAStandards.csv", header=TRUE)
Wax.Stand<-read.csv("Data/WaxStandards.csv", header=TRUE)
SampData<-read.csv("Data/Samples.csv", header=TRUE)


####Sample Meta Data
str(SampData)

##Set factor variables
SampData$TimeP<-factor(SampData$TimeP, levels=c("IN", "TP1", "TP2", "TP3", "TP4"))
SampData$Site<-factor(SampData$Site, levels=c("KL", "SS"))
SampData$Genotype<-factor(SampData$Genotype, levels=c("AC8", "AC10", "AC12"))
SampData$Orig<-factor(SampData$Orig, levels=c("N", "T"))
SampData$Origin<-factor(SampData$Origin, levels=c("Native", "Transplant"))

##Add a Sample Set Variable
SampData$Set<-paste(SampData$TimeP, SampData$Site, SampData$Genotype, SampData$Treat, SampData$Orig, sep=".")

##Add Site.Orig variable
SampData$Site.Orig<-paste(SampData$Site, SampData$Orig, sep=".")
SampData$Site.Orig<-factor(SampData$Site.Orig, levels=c("KL.N", "KL.T", "SS.N", "SS.T"))


```


### Sample Surface Area
```{r}
####Create Standard Curve

##Calculate Surface Area of Cylinders from Standards
Wax.Stand$SA_cm2<-2*pi*(Wax.Stand$Dm_cm/2)*Wax.Stand$Ht_cm+2*pi*(Wax.Stand$Dm_cm/2)^2

##Calculate Difference in Wax Weight
Wax.Stand$Wax.D_g<- Wax.Stand$Wax.F_g-Wax.Stand$Wax.I_g

##Linear Model of SA as a Function of Wax Weight
wax.SA.lm  <- lm(SA_cm2~Wax.D_g, data=Wax.Stand)
summary(wax.SA.lm)
coef(wax.SA.lm)

SA.mod <- function(wax.weight) {
  coefs <- coef(wax.SA.lm)
  #y = mx + b
  SA <- ((coefs[2] * wax.weight) + coefs[1])
  return(SA)}

####Apply Standard Curve

##Calculate Difference in Wax Weight (g) in Sample Data
SampData$Wax.D_g<- SampData$Wax.F_g-SampData$Wax.I_g

##Calculate Surface Area (cm^2) by Applying Linear Model Function
SampData$SA_cm2<-SA.mod(SampData$Wax.D_g)

```


### Subset Sample MetaData by Experiment
```{r}
##Main Corals in the Nursery
Corals_Main<-subset(SampData, Treat=="M")

##Thermal Tolerance Assay
Corals_Therm<-subset(SampData, Treat=="C" | Treat=="H")
```


# Protein

### Calculate Protein Concentration
```{r}
####Create Standard Curve

##Subset Standards Data
Prot.St<- subset(Prot, Input=="Standard")

##Merge Standard Meta Data with Absorbance data
#Merges by Random Number (RandN) column
BCAStands<-merge(BCA.Stand, Prot.St, all.x=TRUE)

##Plot Protein Concentration as a function of Absorbance 
plot(BCAStands$A562, BCAStands$Protein_ug.ml, pch=19)

##Fit Models of Protein Concentration as a function of Absorbance 

#First degree polynomial equation:
BCA.lm  <- lm(Protein_ug.ml~A562, data=BCAStands)
#Second degree polynomial equation:
BCA.ploy2 <- lm(Protein_ug.ml~poly(A562,2,raw=TRUE), data=BCAStands)
#Third degree polynomial equation:
BCA.ploy3 <- lm(Protein_ug.ml~poly(A562,3,raw=TRUE), data=BCAStands)

##Add Models to Plot
xx <- seq(0,3, length=50)

lines(xx, predict(BCA.lm, newdata=data.frame(A562=xx)), col="red")
lines(xx, predict(BCA.ploy2, newdata=data.frame(A562=xx)), col="green")
lines(xx, predict(BCA.ploy3, newdata=data.frame(A562=xx)), col="blue")

##Compare Models for Best Fit
anova(BCA.lm, BCA.ploy2)
#Poly2 is a significantly better fit than linear

anova(BCA.ploy2, BCA.ploy3)
#Poly3 is significantly better fit than Ploy2

##Create a function with the Poly3 model Equation
summary(BCA.ploy3)
coef(BCA.ploy3)

TP.mod <- function(absorbance) {
  coefs <- coef(BCA.ploy3)
  #y = d + cx + bx^2 + ax^3
  protein <- coefs[1] + (coefs[2] * absorbance) + (coefs[3] * absorbance^2) + (coefs[4] * absorbance^3)
  return(protein)}


####Apply Standard Curve

##Subset Sample Data (Unknown Sample)
Prot.Un<- subset(Prot, Input=="Un")

##Calculate Protein Concentration (ug/ml)
Prot.Un$TP_ug.ml<-TP.mod(Prot.Un$A562)

##Merge with Sample Meta Data to Calculate Protein per Surface Area
#Merges by Random Number (RandN) column
#Adds necessary Slurry Volume (Vol_ml) and Surface Area (SA_cm2) columns
#Retains Sample Meta Data only for samples with Protein data (Main samples only)
Prot.Un<-merge(Prot.Un, SampData, all.x=TRUE, all.y=FALSE)

##Calculate Total Protein (ug) 
Prot.Un$TP_ug<-Prot.Un$TP_ug.ml*Prot.Un$Vol_ml

##Calculate Protein per Surface Area (ug/cm^2)
Prot.Un$TP_ug.cm2<-Prot.Un$TP_ug/Prot.Un$SA_cm2

##Separate Coral and Symbiont Fractions
Prot.C<- subset(Prot.Un, Fraction=="C")
Prot.C<-rename(Prot.C, c("TP_ug.cm2_C" = "TP_ug.cm2"))

Prot.S<- subset(Prot.Un, Fraction=="S")
Prot.S<-rename(Prot.S, c("TP_ug.cm2_S" = "TP_ug.cm2"))
```


### Check for Outliers
Check for Outliers by Timepoint, grouped by sample set. Removing any clear outlier samples and outliers of technical replicates before averaging across technical repliates. 

#### Coral Host
```{r}
##Initial Visual Check
ggplot(Prot.C, aes(x=Set, y=TP_ug.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

##Check for Outliers by Timepoint

#TP1
ggplot(subset(Prot.C, TimeP=="TP1"), aes(x=Set, y=TP_ug.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(50,1000)+
  theme(axis.text.x = element_text(angle = 90))

#TP2
ggplot(subset(Prot.C, TimeP=="TP2"), aes(x=Set, y=TP_ug.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(50,1000)+
  theme(axis.text.x = element_text(angle = 90))

Prot.C$RandN[which(Prot.C$TimeP=="TP2" & Prot.C$TP_ug.cm2_C<120)] # "125" "126" "127"

#Month TP3
ggplot(subset(Prot.C, TimeP=="TP3"), aes(x=Set, y=TP_ug.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(100,1000)+
  theme(axis.text.x = element_text(angle = 90))

Prot.C$RandN[which(Prot.C$TimeP=="TP3" & Prot.C$TP_ug.cm2_C>700)] #"186" "187" "188"

#Month TP4
ggplot(subset(Prot.C, TimeP=="TP4"), aes(x=Set, y=TP_ug.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(50,1100)+
  theme(axis.text.x = element_text(angle = 90))

Prot.C$RandN[which(Prot.C$TimeP=="TP4" & Prot.C$TP_ug.cm2_C>600)] #"211" "222" "222" "222"

##Remove Outlier Readings
Prot.C.o<-Prot.C[-c(which((Prot.C$TimeP=="TP2" & Prot.C$TP_ug.cm2_C<120) |
(Prot.C$TimeP=="TP3" & Prot.C$TP_ug.cm2_C>700) |
(Prot.C$TimeP=="TP4" & Prot.C$TP_ug.cm2_C>600))),]

##Visual Check
ggplot(Prot.C.o, aes(x=Set, y=TP_ug.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(100,600)+
  theme(axis.text.x = element_text(angle = 90))

```


#### Symbiont
```{r}
##Initial Visual Check
ggplot(Prot.S, aes(x=Set, y=TP_ug.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

##Check for Outliers by Timepoint
#TP1
ggplot(subset(Prot.S, TimeP=="TP1"), aes(x=Set, y=TP_ug.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(50, 1200)+
  theme(axis.text.x = element_text(angle = 90))

Prot.S$RandN[which(Prot.S$TimeP=="TP1" & Prot.S$TP_ug.cm2_S>750)] #"49" "52" "84"

#TP2
ggplot(subset(Prot.S, TimeP=="TP2"), aes(x=Set, y=TP_ug.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(50,1000)+
  theme(axis.text.x = element_text(angle = 90))

Prot.S$RandN[which(Prot.S$TimeP=="TP2" & Prot.S$TP_ug.cm2_S>500 & Prot.S$Site=="SS" & Prot.S$Genotype=="AC8")] #"129"

#TP3
ggplot(subset(Prot.S, TimeP=="TP3"), aes(x=Set, y=TP_ug.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(50,1000)+
  theme(axis.text.x = element_text(angle = 90))

#TP4
ggplot(subset(Prot.S, TimeP=="TP4"), aes(x=Set, y=TP_ug.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(50,1000)+
  theme(axis.text.x = element_text(angle = 90))

Prot.S$RandN[which(Prot.S$TimeP=="TP4" & Prot.S$TP_ug.cm2_S>750)] #"222" "222" "222"

##Remove Outlier Readings
Prot.S.o<-Prot.S[-c(which((Prot.S$TimeP=="TP1" & Prot.S$TP_ug.cm2_S>750) |
(Prot.S$TimeP=="TP2" & Prot.S$TP_ug.cm2_S>500 & Prot.S$Site=="SS" & Prot.S$Genotype=="AC8") |
(Prot.S$TimeP=="TP4" & Prot.S$TP_ug.cm2_S>750))),]

##Visual Check
ggplot(Prot.S.o, aes(x=Set, y=TP_ug.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(100,750)+
  theme(axis.text.x = element_text(angle = 90))

```


### Add Protein to Main Coral Data
Add host and symbiont fractions for a total holobiont value to be used for downstream analysis.

```{r}
####Average Across Replicate Readings ("Rep" column: A, B, C)
names(Prot.C.o)
Prot.C.a<-aggregate(Prot.C.o$TP_ug.cm2_C, list(Prot.C.o$RandN, Prot.C.o$ID), mean)
names(Prot.C.a)<-c("RandN", "ID", "TP_ug.cm2_C")

names(Prot.S.o)
Prot.S.a<-aggregate(Prot.S.o$TP_ug.cm2_S, list(Prot.S.o$RandN, Prot.S.o$ID), mean)
names(Prot.S.a)<-c("RandN", "ID", "TP_ug.cm2_S")

#### Add Host and Symbiont for Holobiont 
Prot.Hol<-merge(Prot.C.a, Prot.S.a, all.x=TRUE)
Prot.Hol$TP_ug.cm2<-(Prot.Hol$TP_ug.cm2_C + Prot.Hol$TP_ug.cm2_S)

####Merge Averaged Holobiont Protein Data with Coral Main Data
#Merges by Random Number (RandN) and ID columns
#Retains all Main samples
#Retains RandN, ID, TimeP, Site, Genotype, Orig, Origin, Set, and SA_cm2 from Corals_Main
names(Corals_Main)
CoralData<-merge(Corals_Main[,c(1:5, 8:9, 13:14, 16)], Prot.Hol[,c(1:2, 5)], all.x=TRUE)

```


# Biomass

### Calculate Ash Free Dry Weight
```{r}
##Calculate Change in Weight after Burning (g)
Bio$DeltaBurn_g<-Bio$Dried_g-Bio$Burned_g

##Calculate Ash Free Dry Weight (AFDW) (g) per Volume Input of Tissue (ml) 
Bio$AFDW_g.ml<-Bio$DeltaBurn_g/Bio$InVol_ml

##Merge with Sample Meta Data to Calculate Biomass per Surface Area
#Merges by Random Number (RandN) column
#Adds necessary Slurry Volume (Vol_ml) and Surface Area (SA_cm2) columns
#Retains Sample Meta Data only for samples with Biomass data (Main samples only)
Bio<-merge(Bio, SampData, all.x=TRUE, all.y=FALSE)

##Calculate Total AFDW (g) 
Bio$AFDW_g<-Bio$AFDW_g.ml*Bio$Vol_ml

##Calculate AFDW per Surface Area (mg/cm^2)
Bio$AFDW_g.cm2<-Bio$AFDW_g/Bio$SA_cm2
Bio$AFDW_mg.cm2 <- Bio$AFDW_g.cm2 * 1000

##Separate Coral and Symbiont Fractions
Bio.C<-subset(Bio, Fraction=="C")
Bio.C<-rename(Bio.C, c("AFDW_mg.cm2_C" = "AFDW_mg.cm2"))

Bio.S<-subset(Bio, Fraction=="Z")
Bio.S<-rename(Bio.S, c("AFDW_mg.cm2_S" = "AFDW_mg.cm2"))

```


### Check for Outliers
Check for Outliers by Timepoint, grouped by sample set. Removing any clear outlier samples. 

#### Coral Host
```{r}
##Initial Visual Check
ggplot(Bio.C, aes(x=Set, y=AFDW_mg.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

##Check for Outliers by Timepoint

#TP1
ggplot(subset(Bio.C, TimeP=="TP1"), aes(x=Set, y=AFDW_mg.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP2
ggplot(subset(Bio.C, TimeP=="TP2"), aes(x=Set, y=AFDW_mg.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP3
ggplot(subset(Bio.C, TimeP=="TP3"), aes(x=Set, y=AFDW_mg.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP4
ggplot(subset(Bio.C, TimeP=="TP4"), aes(x=Set, y=AFDW_mg.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,3.5)+
  theme(axis.text.x = element_text(angle = 90))

Bio.C$RandN[which(Bio.C$TimeP=="TP4" & Bio.C$AFDW_mg.cm2_C>3)] #222 #Also outlier for Protein

##Remove Outliers 
Bio.C.o<-Bio.C[-c(which(Bio.C$TimeP=="TP4" & Bio.C$AFDW_mg.cm2_C>3)),]

##Visual Check
ggplot(Bio.C.o, aes(x=Set, y=AFDW_mg.cm2_C)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))

```



#### Symbiont
```{r}
##Initial Visual Check
ggplot(Bio.S, aes(x=Set, y=AFDW_mg.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

##Check for Outliers by Timepoint

#TP1
ggplot(subset(Bio.S, TimeP=="TP1"), aes(x=Set, y=AFDW_mg.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP2
ggplot(subset(Bio.S, TimeP=="TP2"), aes(x=Set, y=AFDW_mg.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP3
ggplot(subset(Bio.S, TimeP=="TP3"), aes(x=Set, y=AFDW_mg.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP4
ggplot(subset(Bio.S, TimeP=="TP4"), aes(x=Set, y=AFDW_mg.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2)+
  theme(axis.text.x = element_text(angle = 90))

Bio.S$RandN[which(Bio.S$TimeP=="TP4" & Bio.S$AFDW_mg.cm2_S>1.5)] #222 #Also outlier for Protein and Biomass of Host


##Remove Outliers 
Bio.S.o<-Bio.S[-c(which(Bio.S$TimeP=="TP4" & Bio.S$AFDW_mg.cm2_S>1.5)),]

##Visual Check
ggplot(Bio.S.o, aes(x=Set, y=AFDW_mg.cm2_S)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1.5)+
  theme(axis.text.x = element_text(angle = 90))

```


### Add Biomass to Main Coral Data
Add host and symbiont fractions for a total holobiont value to be used for downstream analysis.

```{r}
#### Add Host and Symbiont for Holobiont 
Bio.Hol<-merge(Bio.C.o[,c("ID", "RandN",  "AFDW_mg.cm2_C")], Bio.S.o[,c("ID", "AFDW_mg.cm2_S")], all.x=TRUE)
Bio.Hol$AFDW_mg.cm2<-(Bio.Hol$AFDW_mg.cm2_C + Bio.Hol$AFDW_mg.cm2_S)

####Merge Averaged Holobiont Biomass Data with Coral Main Data
#Merges by ID column and adds AFDW (mg/cm^2) (AFDW_mg.cm2) column from Biomass dataframe
#Retains all Main samples
CoralData<-merge(CoralData, Bio.Hol[,c(1:2, 5)], all.x=TRUE)

```


# Chlorophyll

### Calculate Chlorophyll Concentration
Equations for Dinos from Jeffrey and Humphrey 1975 in 100% acetone
Chla = 11.43 * A663 - 0.64 * A630
Chlc2 = 27.09 * A630 - 3.63 * A663
```{r}
##Subtract Background A750 from A630 and A663
Chl$A630.c<-Chl$A630-Chl$A750
Chl$A663.c<-Chl$A663-Chl$A750

##Divide by Pathlength (0.5cm pathlength for 175ul sample in UVStar Plate) 
Chl$A630.c<-c(Chl$A630.c/0.5)
Chl$A663.c<-c(Chl$A663.c/0.5)

##Calculate Chl-a and Chl-c2 in ug/ml
Chl$Chl.a_ug.ml<-11.43*Chl$A663.c- 0.64*Chl$A630.c
Chl$Chl.c2_ug.ml <- 27.09*Chl$A630.c - 3.63*Chl$A663.c

##Merge with Sample Data to Calculate Chlorophyll per Surface Area
#Merges by Random Number (RandN) column
#Adds necessary Slurry Volume (Vol_ml) and Surface Area (SA_cm2) columns
Chl<-merge(Chl, SampData,  all=TRUE)

##Calculate Total Chlorophyll-a and c2 (ug) 
Chl$Chl.a_ug<-Chl$Chl.a_ug.ml*Chl$Vol_ml
Chl$Chl.c2_ug<-Chl$Chl.c2_ug.ml*Chl$Vol_ml

##Calculate Chlorophyll-a and c2 per Surface Area (ug/cm^2)
Chl$Chl.a_ug.cm2<-Chl$Chl.a_ug/Chl$SA_cm2
Chl$Chl.c2_ug.cm2<-Chl$Chl.c2_ug/Chl$SA_cm2

##Initial Visual Check
ggplot(Chl, aes(x=Set, y=Chl.a_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

ggplot(Chl, aes(x=Set, y=Chl.c2_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

##Set Negative Values to Zero
Chl$Chl.a_ug.cm2[(which(Chl$Chl.a_ug.cm2<0))]<-0
Chl$Chl.c2_ug.cm2[(which(Chl$Chl.c2_ug.cm2<0))]<-0

##Add Chlorophyll-a and c2 for Total Chlorophyll per Surface Area (ug/cm^2)
Chl$Chl_ug.cm2<-Chl$Chl.a_ug.cm2+Chl$Chl.c2_ug.cm2

##Visual Check
ggplot(Chl, aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

```


### Check for Outliers
Check for Outliers by Treatment and Timepoint, grouped by sample set. Removing clear outlier samples and outliers of technical replicates before averaging across technical repliates. 

#### Main
```{r}
##Subset Main Corals
Chl.M<-subset(Chl, Treat=="M")

#TP1
ggplot(subset(Chl.M, TimeP=="TP1"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))


#TP2
ggplot(subset(Chl.M, TimeP=="TP2"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,4.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP3
ggplot(subset(Chl.M, TimeP=="TP3"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,4.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP4
ggplot(subset(Chl.M, TimeP=="TP4"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,7.5)+
  theme(axis.text.x = element_text(angle = 90))

Chl.M$RandN[which(Chl.M$TimeP=="TP4" & Chl.M$Chl_ug.cm2>6)] #"222" "222" "222" #Also outlier for Protein and Biomass

##Remove Outliers 
Chl.M.o<-Chl.M[-c(which(Chl.M$TimeP=="TP4" & Chl.M$Chl_ug.cm2>6)),]

```


#### Control
```{r}
##Subset Control Treatment in Thermal Tolerance Assay 
Chl.C<-subset(Chl, Treat=="C")

#IN
ggplot(subset(Chl.C, TimeP=="IN"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))

Chl.C$RandN[which(Chl.C$TimeP=="IN" & Chl.C$Chl_ug.cm2<0.25)] #"W2_45"

#TP1
ggplot(subset(Chl.C, TimeP=="TP1"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP2
ggplot(subset(Chl.C, TimeP=="TP2"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.5)+
  theme(axis.text.x = element_text(angle = 90))

#TP3
ggplot(subset(Chl.C, TimeP=="TP3"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,3.5)+
  theme(axis.text.x = element_text(angle = 90))

Chl.C$RandN[which(Chl.C$TimeP=="TP3" & Chl.C$Chl_ug.cm2>2.5)] #"M8_33" "M8_33" "M8_33" 

#TP4
ggplot(subset(Chl.C, TimeP=="TP4"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,4)+
  theme(axis.text.x = element_text(angle = 90))

##Remove Outliers 
Chl.C.o<-Chl.C[-c(which((Chl.C$TimeP=="IN" & Chl.C$Chl_ug.cm2<0.25)| 
                          (Chl.C$TimeP=="TP3" & Chl.C$Chl_ug.cm2>2.5))),]

```


#### Heated
```{r}
##Subset Heated Treatment in Thermal Tolerance Assay
Chl.H<-subset(Chl, Treat=="H")

#IN
ggplot(subset(Chl.H, TimeP=="IN"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1)+
  theme(axis.text.x = element_text(angle = 90))

Chl.H$RandN[which(Chl.H$TimeP=="IN" & Chl.H$Chl_ug.cm2>0.75)] #"W2_88" "W2_88" "W2_88"

#TP1
ggplot(subset(Chl.H, TimeP=="TP1"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1)+
  theme(axis.text.x = element_text(angle = 90))

#TP2
ggplot(subset(Chl.H, TimeP=="TP2"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1)+
  theme(axis.text.x = element_text(angle = 90))

#TP3
ggplot(subset(Chl.H, TimeP=="TP3"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2)+
  theme(axis.text.x = element_text(angle = 90))

Chl.H$RandN[which(Chl.H$TimeP=="TP3" & Chl.H$Chl_ug.cm2>1.5 & Chl.H$Genotype=="AC10")] #"M8_11" "M8_11"

#TP4
ggplot(subset(Chl.H, TimeP=="TP4"), aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1)+
  theme(axis.text.x = element_text(angle = 90))

Chl.H$RandN[which(Chl.H$TimeP=="TP4" & Chl.H$Chl_ug.cm2>0.5)] #"M12_63" "M12_63" "M12_63"

##Remove Outliers
Chl.H.o<-Chl.H[-c(which((Chl.H$TimeP=="IN" & Chl.H$Chl_ug.cm2>0.75) |
(Chl.H$TimeP=="TP3" & Chl.H$Chl_ug.cm2>1.5 & Chl.H$Genotype=="AC10") | 
(Chl.H$TimeP=="TP4" & Chl.H$Chl_ug.cm2>0.50))),]

```


### Add Chlorophyll to Main and Thermal Datasets
```{r}
##Recombine Cleaned Chlorophyll dataframes
Chl.o<-rbind(Chl.M.o, Chl.C.o, Chl.H.o)

ggplot(Chl.o, aes(x=Set, y=Chl_ug.cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))


##Average Across Replicate Readings ("Rep" column: A, B, C)
names(Chl.o)
Chl.a<-aggregate(Chl.o$Chl_ug.cm2, list(Chl.o$RandN, Chl.o$ID), mean)
names(Chl.a)<-c("RandN", "ID", "Chl_ug.cm2")

##Add Total Chlorophyll to Main Coral Data and Thermal Tolerance Data

##Merge Averaged Chlorophyll Data with Coral Main Data
#Merges by Random Number (RandN) and ID columns
#Retains all Main samples
names(Chl.a)
CoralData<-merge(CoralData, Chl.a, all.x=TRUE, all.y=FALSE)

##Merge Averaged Chlorophyll Data with Thermal Tolerance Data
#Merges by Random Number (RandN) and ID columns
#Retains all Thermal Tolerance Assay samples
#Retains RandN, ID, TimeP, Site, Genotype, Treat, Treatment, Orig, Origin, Set, and SA_cm2 from Corals_Therm
names(Corals_Therm)
ThermData<-merge(Corals_Therm[,c(1:9, 13:14, 16)], Chl.a, all.x=TRUE, all.y=FALSE)

```


# Symbionts

### Calculate Symbiont Density
```{r}
####Calculate Dilution Factors

#Scales for 1:10 Dilution Sent for Flow Cytometry
Sym$Send_df<-Sym$SendInputVol_ul/Sym$SendTotalVol_ul

##Scales for Resuspending Symbiont Pellet based on Volume of 0.01% SDS Used
Sym$Resp_df<-Sym$InputVol_ul/Sym$RespVol_ul

####Calculate Symbiont Density

##Scale Flow Cy Count/ul to account for Dilution Factor applied at Flow Cy Center
Sym$Count_ul_scaled_FC_df<-Sym$Count_ul/Sym$FC_df

##Scale Flow Cy Count/ul to account for Sent Dilution Factor
Sym$Count_ul_scaled_send_df<-Sym$Count_ul_scaled_FC_df/Sym$Send_df

##Scale Flow Cy Count/ul to account for Resuspension Dilution Factor
Sym$Count_ul_scaled_resp_df<-Sym$Count_ul_scaled_send_df/Sym$Resp_df

##Merge with Sample Data to Calculate Symbionts per Surface Area
#Merges by Random Number (RandN) column
#Adds necessary Slurry Volume (Vol_ml) and Surface Area (SA_cm2) columns
#Retains Sample Meta Data only for samples with Symbiont data (Thermal Assay samples only)
Sym<-merge(Sym, SampData, all.x=TRUE, all.y=FALSE)

##Calculate Total Symbiont Count (scaling to Slurry Total Volume in ul)
Sym$Count_total<-Sym$Count_ul_scaled_resp_df*(Sym$Vol_ml*1000)

##Calculate Symbionts per Surface Area
Sym$Sym_cm2<-Sym$Count_total/Sym$SA_cm2

##Scale to Symb * 10^6 / cm^2
Sym$Sym10.6_cm2<-Sym$Sym_cm2/10^6

##Initial Visual Check
ggplot(Sym, aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

```


### Check for Outliers
Check for Outliers by Treatment and Timepoint, grouped by sample set. Removing outliers of technical replicates before averaging across technical repliates. 

#### Control
```{r}
##Subset Control Treatment in Thermal Tolerance Assay
Sym.C<-subset(Sym, Treat=="C")
Sym.C<-Sym.C[-c(which(is.na(Sym.C$Sym10.6_cm2))),]

#IN
ggplot(subset(Sym.C, TimeP=="IN"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2)+
  theme(axis.text.x = element_text(angle = 90))

#TP1
ggplot(subset(Sym.C, TimeP=="TP1"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2)+
  theme(axis.text.x = element_text(angle = 90))

#TP2
ggplot(subset(Sym.C, TimeP=="TP2"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2)+
  theme(axis.text.x = element_text(angle = 90))

#TP3
ggplot(subset(Sym.C, TimeP=="TP3"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2)+
  theme(axis.text.x = element_text(angle = 90))

#TP4
ggplot(subset(Sym.C, TimeP=="TP4"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2)+
  theme(axis.text.x = element_text(angle = 90))

```


#### Heated
```{r}
##Subset Heated Treatment in Thermal Tolerance Assay
Sym.H<-subset(Sym, Treat=="H")

#IN
ggplot(subset(Sym.H, TimeP=="IN"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1)+
  theme(axis.text.x = element_text(angle = 90))

#TP1
ggplot(subset(Sym.H, TimeP=="TP1"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1)+
  theme(axis.text.x = element_text(angle = 90))

Sym.H$RandN[which(Sym.H$TimeP=="TP1" & Sym.H$Sym10.6_cm2>0.75)] #"M1_73" "M1_73"

#TP2
ggplot(subset(Sym.H, TimeP=="TP2"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1.5)+
  theme(axis.text.x = element_text(angle = 90))

Sym.H$RandN[which(Sym.H$TimeP=="TP2" & Sym.H$Sym10.6_cm2>0.75)] #"M4_61" "M4_85"

#TP3
ggplot(subset(Sym.H, TimeP=="TP3"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,2.1)+
  theme(axis.text.x = element_text(angle = 90))

Sym.H$RandN[which(Sym.H$TimeP=="TP3" & Sym.H$Sym10.6_cm2>1.8)] #"M8_42"

#TP4
ggplot(subset(Sym.H, TimeP=="TP4"), aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0,1)+
  theme(axis.text.x = element_text(angle = 90))

##Remove Outliers
Sym.H.o<-Sym.H[-c(which((Sym.H$TimeP=="TP1" & Sym.H$Sym10.6_cm2>0.75) | 
                          (Sym.H$TimeP=="TP2" & Sym.H$Sym10.6_cm2>0.75) |
                          (Sym.H$TimeP=="TP3" & Sym.H$Sym10.6_cm2>1.8))),]

```


### Add Symbionts to Thermal Data
```{r}
##Recombine Cleaned Symbionts dataframes
Sym.o<-rbind(Sym.C, Sym.H.o)

##Visual Check
ggplot(Sym.o, aes(x=Set, y=Sym10.6_cm2)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

##Average Across Replicate Readings ("Rep" column: A, B, C)
names(Sym.o)
Sym.a<-aggregate(Sym.o$Sym10.6_cm2, list(Sym.o$RandN, Sym.o$ID), mean)
names(Sym.a)<-c("RandN", "ID", "Sym10.6_cm2")

##Add Symbiont Density to Thermal Tolerance Data

##Merge Averaged Symbiont Data with Thermal Tolerance Data
#Merges by Random Number (RandN) and ID columns
#Retains all Thermal Tolerance Assay samples
names(ThermData)
ThermData<-merge(ThermData, Sym.a, all.x=TRUE, all.y=FALSE)

```


# Fv/Fm

### Organize Data
```{r}
##Merge PAM Meta Data with PAM Data
#Merges by Memory Number (Memory) column
#Retains PAM Data only for relevant measurements with Meta Data 
PAM<-merge(PAM_Meta, PAM, all.x=TRUE, all.y=FALSE)

PAM<-PAM[-c(which(is.na(PAM$Fv_Fm))),]

##Merge PAM Data with Sample Data
#Merges by ID column
#Retains Sample Meta Data only for samples with Fv/Fm data (Thermal Assay samples only)
PAM<-merge(PAM, SampData, all.x=TRUE, all.y=FALSE)

##Initial Visual Check
ggplot(PAM, aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))

```


### Check for Outliers
Check for Outliers by Treatment and Timepoint, grouped by sample set. Removing outliers of technical replicates before averaging across technical repliates. 

#### Control
```{r}
##Subset Control Treatment in Thermal Tolerance Assay
PAM.C<-subset(PAM, Treat=="C")

#IN
ggplot(subset(PAM.C, TimeP=="IN"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.45,0.75)+
  theme(axis.text.x = element_text(angle = 90))

PAM.C$RandN[which(PAM.C$TimeP=="IN" & PAM.C$Fv_Fm<0.5)] # "W2_93" 

#TP1
ggplot(subset(PAM.C, TimeP=="TP1"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.45,0.75)+
  theme(axis.text.x = element_text(angle = 90))

#TP2
ggplot(subset(PAM.C, TimeP=="TP2"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.45,0.75)+
  theme(axis.text.x = element_text(angle = 90))

PAM.C$RandN[which(PAM.C$TimeP=="TP2" & PAM.C$Fv_Fm<0.53)] # "M4_91"

#TP3
ggplot(subset(PAM.C, TimeP=="TP3"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.45,0.75)+
  theme(axis.text.x = element_text(angle = 90))

#TP4
ggplot(subset(PAM.C, TimeP=="TP4"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.45,0.75)+
  theme(axis.text.x = element_text(angle = 90))

##Remove Outliers
PAM.C.o<-PAM.C[-c(which((PAM.C$TimeP=="IN" & PAM.C$Fv_Fm<0.5) | (PAM.C$TimeP=="TP2" & PAM.C$Fv_Fm<0.53))),]

```




#### Heated
```{r}
##Subset Heated Treatment in Thermal Tolerance Assay
PAM.H<-subset(PAM, Treat=="H")

#IN
ggplot(subset(PAM.H, TimeP=="IN"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.25,0.7)+
  theme(axis.text.x = element_text(angle = 90))

PAM.H$RandN[which(PAM.H$TimeP=="IN" & PAM.H$Fv_Fm<0.5 &  PAM.H$Site=="SS")] # "W2_94" "W2_94"


#TP1
ggplot(subset(PAM.H, TimeP=="TP1"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.25,0.7)+
  theme(axis.text.x = element_text(angle = 90))

PAM.H$RandN[which(PAM.H$TimeP=="TP1" & PAM.H$Fv_Fm<0.35)] # "M1_86"

#TP2
ggplot(subset(PAM.H, TimeP=="TP2"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.25,0.7)+
  theme(axis.text.x = element_text(angle = 90))

PAM.H$RandN[which(PAM.H$TimeP=="TP2" & PAM.H$Fv_Fm<0.35 &  PAM.H$Site=="SS")] # "M4_84"

#TP3
ggplot(subset(PAM.H, TimeP=="TP3"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.25,0.7)+
  theme(axis.text.x = element_text(angle = 90))

PAM.H$RandN[which(PAM.H$TimeP=="TP3" & PAM.H$Fv_Fm<0.45)] # "M8_83"

#TP4
ggplot(subset(PAM.H, TimeP=="TP4"), aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  ylim(0.2,0.7)+
  theme(axis.text.x = element_text(angle = 90))


##Remove Outliers 
PAM.H.o<-PAM.H[-c(which((PAM.H$TimeP=="IN" & PAM.H$Fv_Fm<0.5 &  PAM.H$Site=="SS") | 
                          (PAM.H$TimeP=="TP1" & PAM.H$Fv_Fm<0.35)|
              (PAM.H$TimeP=="TP2" & PAM.H$Fv_Fm<0.35 &  PAM.H$Site=="SS") |
                (PAM.H$TimeP=="TP3" & PAM.H$Fv_Fm<0.45))),]

```

### Add Fv/Fm to Thermal Data
```{r}
##Recombine Cleaned PAM dataframes
PAM.o<-rbind(PAM.C.o, PAM.H.o)

ggplot(PAM.o, aes(x=Set, y=Fv_Fm)) + 
  geom_boxplot(alpha=0.5, shape=2, outlier.shape = NA)+
  geom_jitter(shape=16, position=position_jitter(0.1))+
  theme(axis.text.x = element_text(angle = 90))


##Average Across Replicate Readings ("Rep" column: A, B, C)
names(PAM.o)
PAM.a<-aggregate(PAM.o$Fv_Fm, list(PAM.o$ID), mean)
names(PAM.a)<-c("ID", "Fv_Fm")

##Add Fv/Fm to Thermal Tolerance Data

##Merge Averaged Fv/Fm Data with Thermal Tolerance Data
#Merges by ID column
#Retains all Thermal Tolerance Assay samples
names(ThermData)
ThermData<-merge(ThermData, PAM.a, all.x=TRUE, all.y=FALSE)

```


# Write Out Datasets
```{r}
##Main Coral Data
write.csv(CoralData, "Outputs/CoralData.csv", row.names=FALSE)

##Thermal Tolerance Assay
write.csv(ThermData, "Outputs/ThermData.csv", row.names=FALSE)

```

